Litigant Framing Data

### 2022-05-05 data-cleaning/09-scrape-litigant-text.Rmd
scrape litigant briefs

---
title: "Tidy Amicus Data"
author: "Amanda Konet"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

There are ~40 folders in Amicus IV > data > amicus files. For each amicus file (denoted by files with "amicus" or "amici" in the file name), copy the file ID, file name, case name, and file text into a CSV.

@@

Set working directory to amcius files folder

```{r}
box_setwd("146066009084")
```

@@

  # in each case folder, grab the name and id of the decision file
  file_ids <-
    foreach(i = it,
            .combine = rbind,
            .inorder = F) %dopar% {
              i %>%
                filter(grepl("amicus|amici", name, ignore.case = T)) %>%
                select(case, name, id)
            }
  print("Obtained amicus file ids")

@@

# run the function for Abortion and Sex Discrim folders
amicus_file_ids <- all_file_names(case_folders)

@@

```{r}
# save this file to data > processed amicus files
amicus_file_ids %>% 
  right_join(., case_folders, "case") %>% 
  group_by(case) %>% 
  summarize(n = sum(grepl("amicus|amici", name, ignore.case = T))) %>% 
  arrange(case) #%>% 
  #box_write(., "amicus brief counts.xlsx", dir_id = "145990409196")
```

@@

```{r}
amicus_file_ids %>% 
  right_join(., case_folders, "case") %>% 
  select(-id.y) %>% 
  rename(id = id.x) %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
  box_write(., "amicus-file-ids.csv", dir_id = "145990409196")
```

@@

Obtain the raw text from each amicus brief. Note that we have two file types here: DOCX & PDF.

@@

```{r}
amicus_file_ids <- amicus_file_ids %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) 
amicus_file_ids %>% group_by(file_type) %>% summarize(n = n())
```

```{r}
# create iterator 
itd <- iter(amicus_file_ids, by = "row")

@@

  # grab text and concat to string
  #txt <- box_read(
  #  file_id = id,
  #  read_fun = function(x)
  #    textreadr::read_document(x)
  #)

@@

```{r}
amicus_txt %>% 
  mutate(txt_full = str_squish(txt_full),
         summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
  group_by(summary) %>% 
  summarize(n=n())
```

@@

```{r}
amicus_txt %>% 
  mutate(txt_full = str_squish(txt_full),
         summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
  filter(!summary) %>% 
  select(brief)
```

@@

```{r}
box_write(amicus_txt,
          file_name = "raw-amicus-brief-text.csv",
          dir_id = '145990409196')
```

>>>>

---
title: "Litigant Framing Data"
author: "Amanda Konet and Sarah Torrence"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

There are ~40 folders in Supreme Court > Sup Ct - Abortion Cases. For each amicus file (NOT denoted by files with "amicus”, “amici”, “decision”, “reply”, “appendix”, and “oral” in the file name), copy the file ID, file name, case name, and file text into a CSV.

@@

Set working directory to  files folder

```{r}
box_setwd("6932017842")
```

@@

  # in each case folder, grab the name and id of the decision file
  file_ids <-
    foreach(i = it,
            .combine = rbind,
            .inorder = F) %dopar% {
              i %>%
                filter(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T)) %>%
                select(case, name, id)
            }
  print("Obtained litigant file ids")

@@

# run the function for Abortion and Sex Discrim folders
litigant_file_ids <- all_file_names(case_folders)

@@

```{r}
# save this file to data > processed amicus files
litigant_file_ids %>% 
  right_join(., case_folders, "case") %>% 
  group_by(case) %>% 
  summarize(n = sum(!grepl("amicus|amici|decision|reply|appendix|oral", name, ignore.case = T))) %>% 
  arrange(case) #%>% 
  #box_write(., "amicus brief counts.xlsx", dir_id = "145990409196")
```

@@

```{r}
# amicus_file_ids %>% 
#   right_join(., case_folders, "case") %>% 
#   select(-id.y) %>% 
#   rename(id = id.x) %>% 
#   mutate(file_type = tolower(sub(".*\\.", "", name))) %>% 
#   box_write(., "amicus-file-ids.csv", dir_id = "145990409196")
```

@@

Obtain the raw text from each amicus brief. Note that we have two file types here that we want: DOCX & PDF. All other duplicate folders and extra types can be filtered out.

@@

```{r}
litigant_file_ids <- litigant_file_ids %>% 
  mutate(file_type = tolower(sub(".*\\.", "", name))) 
litigant_file_ids %>% group_by(file_type) %>% summarize(n = n())
```

```{r}
litigant_file_ids <- litigant_file_ids %>% filter(file_type == 'docx' | file_type == 'pdf')
```

```{r}
# create iterator 
itd <- iter(litigant_file_ids, by = "row")

@@

  # grab text and concat to string
  # txt <- box_read(
  #  file_id = id,
  #  read_fun = function(x)
  #    textreadr::read_document(x)
  # )

@@

```{r}
# amicus_txt %>% 
#   mutate(txt_full = str_squish(txt_full),
#          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
#   group_by(summary) %>% 
#   summarize(n=n())
```

@@

```{r}
# amicus_txt %>% 
#   mutate(txt_full = str_squish(txt_full),
#          summary = grepl("summary of argument|summary of the argument", txt_full, ignore.case = T)) %>%
#   filter(!summary) %>% 
#   select(brief)
```

@@

```{r}
box_write(amicus_txt,
          file_name = "raw-litigant-brief-text.csv",
          dir_id = '145990409196')
```
